Assignment 5

### 2015-02-24 rmtw/a5/latex8.tex
finish rel work

>>>>

Mattsson et al. \cite{mattsson2009linking} discuss the correlation between MDSD and software architecture. The idea that MDSD is benefitial if done right is presented, and one important factor brought up is the need of automatic enforcment of architectural rules \cite{mattsson2009linking}. If this has to be done manually, it will become a bottleneck in large MDSD projects \cite{mattsson2009linking}.
